\beginsong{Father and Son}[by={Cat Stevens}]

\beginverse
It's not \[G]time to make a \[D]change. Just re\[C]lax, take it \[Am]easy.
You're still \[G]young, that's your \[Em]fault,
There's so \[Am]much you have to \[D]know.
Find a \[G]girl, settle \[D]down, if you \[C]want to you can \[Am]marry.
Look at \[G]me, I am \[Em]old, but I'm hap\[Am]py. \[C] \[D]
\endverse

\beginverse
I was \[G]once like you are \[D]now, and I \[C]know that it's not \[Am7]easy,
To be \[G]calm when you've \[Em]found something going \[Am]on. \[C] \[D]
But take your \[G]time, think a \[D]lot,
Why, think of \[C]everything you've \[Am7]got.
For you will \[G]still be here to\[Em]morrow, but your \[D]dreams may \[G]not.
\endverse

\beginverse
How can \[G]I try to ex\[Bm]plain, when I \[C]do he turns a\[Am7]way again.
It's \[G]always been the \[Em]same, same old \[Am]story. \[C] \[D]
From the \[G]moment I could \[Bm]talk I was \[C]ordered to \[Am7]listen 
now there's a \[G]way and I \[Em]know that I \[D]have to \[G]go away.
I \[D]know I \[C]have to \[G]go.
\endverse

\beginverse
It's not \[G]time to make a \[D]change. Just sit \[C]down, take it \[Am]slowly.
You're still \[G]young, that's your \[Em]fault,
There's so \[Am]much you have to \[D]go through.
Find a \[G]girl, settle \[D]down, if you \[C]want you can \[Am]marry.
Look at \[G]me, I am \[Em]old, but I'm ha\[Am]ppy. \[C] \[D]
\endverse

\beginverse
All the \[G]times that I \[Bm]cried, keeping \[C]all the things I \[Am]knew inside,
It's \[G]hard, but it's \[Em]harder to \[Am]ignore it. \[C] \[D]
If they were \[G]right, I'd a\[Bm]gree, but it's \[C]them you know not \[Am]me.
Now there's a \[G]way and I \[Em]know that I \[D]have to \[G]go away.
I \[D]know I \[C]have to \[G]go. 
\endverse
\endsong