\beginsong{Home}[by={Edward Sharpe and the Magnetic Zeros}]

\beginverse*
\nolyrics{Intro: (with whistling) Bm D D/F# D G (x 2)}
\endverse

\beginverse
\textit{Her:}
[Bm]Alabama, Arkansas,
[D]I do love my ma and pa,
[D/F#]Not the way that I do love [G]you.
\endverse

\beginverse
\textit{Him:}
Well, [Bm]Holy, Moley, me, oh my,
[D]You're the apple of my eye,
[D/F#]Girl I've never loved one like [G]you.
\endverse

\beginverse
\textit{Her:}
[Bm]Man oh man you're my best friend,
I [D]scream it to the nothingness,
[D/F#] There ain't nothing that I [G]need.
\endverse

\beginverse
\textit{Him:}
Well, [Bm]hot and heavy, pumpkin pie,
[D]Chocolate candy, Jesus Christ,
[D/F#]Ain't nothing please me more than [G]you.
\endverse

\beginverse
\textit{Both:}
(Ahh [Bm]Home. Let me come [D]home
[D/F#]Home is wherever I'm with [G]you.) x 2
\endverse

\beginverse*
\nolyrics{Em D A \textit{Trumpet Section} (x 3)}
[Bm]La, la, [A]la, la, [Em]take me [G]home.
[A]Mother, I'm coming home.
\vspace{4mm}
(A|---0-2-4---| \textit{(three note re-start)}
Bm D D/F# G \textit{(whistling)}) x 2
\endverse

\beginverse
\textit{Him:}
I'll [Bm]follow you into the park,
[D]Through the jungle through the dark,
[D/F#]Girl I never loved one like [G]you.
\endverse

\textit{Her:}
[Bm]Moats and boats and waterfalls,
[D]Alley-ways and pay phone calls,
[D/F#] I've been everywhere with [G]you.

\textit{Him:}
That's true,
We [Bm]laugh until we think we’ll die,
[D]Barefoot on a summer night
[D/F#]Nothin’ new is sweeter than with [G]you

\textit{Her:}
And [Bm]in the streets you run afree,
[D]Like it's only you and me,
[Both:]
[D/F#] Geeze, you're something to [G]see.

\textit{Both:}
Ahh [Bm]Home. Let me come [D]home
[D/F#]Home is wherever I'm with [G]you.
x2

Em D A
x3

[Bm]La, la, [A]la, la, [Em]take me [G]home.
[A]Mother, I'm coming home.

A|---0-2-4---| \textit{(three note re-start)}
Bm D D/F# G \textit{(Talking)}
x4

\textit{Him:} Jade
\textit{Her:} Alexander
\textit{Him:} Do you remember that day you fell outta my window?
\textit{Her:} I sure do, you came jumping out after me.
\textit{Him:} Well, you fell on the concrete, nearly broke your ass, you were bleeding all over the place and I rushed you out to the hospital, you remember that?
\textit{Her:} Yes I do.
\textit{Him:} Well there's something I never told you about that night.
\textit{Her:} What didn't you tell me?
\textit{Him:} While you were sitting in the backseat smoking a cigarette you thought was gonna be your last, I was falling deep, deeply in love with you, and I never told you til just now.

\textit{Both x2 then him then her (total 4 times)}
Ahh [Bm]Home. Let me come [D]home
[D/F#]Home is wherever I'm with [G]you.

\textit{Her:}
[Bm]Alabama, Arkansas,[D]
[D/F#]I do love my ma and pa...[G]
[Bm]Moats and boats and waterfalls,[D]
[D/F#]Alley-ways and pay phone calls...[D]

\textit{Both:}
[Bm]Home... [D]Home
[D/F#]Home is when I'm alone with [G]you.
x2


capo{3 (optional)}
\beginverse
\[D]One, two, three, four
\[Bm]Tell me that you \[A]love me more
\[D]Sleepless long nights
\[Bm]That is what my \[A]youth was for
\endverse
\beginverse
\[D]Old teenage hopes are a\[Bm]live at your \[A]door
\[D]Left you with nothing but \[Bm]they want some \[A]more
\endverse
\beginchorus
\[A]Ooo-o-oh, you're \[G]changing your heart
\[A]Ooo-o-oh, You \[G]know who you are
\endchorus
\beginverse
\[D]Sweetheart bitterheart \[Bm]now I can't tell \[A]you apart
\[D]Cozy and cold, \[Bm]put the horse be\[A]fore the cart
\[D]Those teenage hopes who have \[Bm]tears in their \[A]eyes
\[D]Too scared to own up to \[Bm]one little \[A]lie
\endverse
\textnote{Repeat Chorus}
\beginverse
\[D]One, two, three, four, 
\[Bm]five, six, \[A]nine, or ten
\[D]Money can't buy you 
\[Bm]back the love that \[A]you had the\[D]-en \[Bm] \[A] \[D] \[Bm] \[A]
\endverse
\beginverse*
\textnote{Repeat Chorus (x2)}
 \[D] \[Bm] \[A]Ooo-o-oh, you know who you \[D]are \[Bm] \[A]
\endverse
\beginverse
\[A]Fo-or the teen\[D]age boys \[Bm]
\[A] They're breaking your \[D]heart
\[A]Fo-or the teen\[D]age boys \[Bm]
\[A] They're breaking your \[D]heart
\[D] \[Bm] \[A] 
\endverse
\endsong
