\beginsong{Home for a rest}[by={Spirit of the West}]

\beginverse\memorize
You'll \[Am]have to ex\[G]cuse me, I'm \[C]not at my \[F]best
I've been \[C]gone for a \[G]month
I've been \[F]drunk since I \[C]left.
These \[Am]so-called va\[G]cations will \[C]soon be my \[F]death
I'm so \[C]sick from the \[G]drink
I need \[F]home for a \[C]rest....
\endverse

\beginverse
We ar^rived in De^cember and ^London was ^cold,
We ^stayed in the ^bars along ^Jarring cross ^road.
We ^never saw ^nothing but ^brass-tops and ^oak.
Kept a ^shine on the ^bar with the ^sleeves of our \[G]coats.
\endverse

\beginchorus 
You'll \[G]have to excuse me, I'm \[C]not at my \[G]best
I've been \[C]gone for a \[F]week
I've been \[G]drunk since I left
And these \[G]so-called vacations
Will \[C]soon be my \[G]death
I'm so \[C]sick from the \[F]drink
I need \[G]home for a \[F]rest
...Take me \[Am]home! \[Dm] \[G] \[Em]
\[Am] \[Dm] \[G] \[Em]
\endchorus

\beginverse
\[Am] Euston \[G]station, the \[C]train heading \[F]North,
\[Am] In the buffet \[G]car we \[F]lurched back and \[G]forth.
Past \[Am]old crooked \[G]dykes through \[C]Yorkshire's green \[F]fields
We were \[C]flung into \[G]dance as the \[F]train jigged and \[G]reeled.
\endverse

\textnote{Repeat Chorus}

\beginverse
By the \[Am]light of the \[G]moon, she'd \[C]drift through the \[F]streets,
A \[C]rare old per\[G]fume, so \[F]seductive and \[G]sweet
She'd \[Am]tease us and \[G]flirt as the \[C]pubs all close \[F]down,
Then \[C]walk us on \[G]home and \[F]deny us a \[G]round.
\endverse

\textnote{Repeat Chorus}

\beginverse
The \[Am]gas heater's \[G]empty, it's \[C]damp as a \[F]tomb
The \[C]spirits we \[G]drank now \[F]ghosts in the \[G]room
I'm \[Am]knackered a\[G]gain, come on, \[C]please take me \[F]soon,
And \[C]don't lift my \[G]head til the \[F]twelve bells at \[G]noon!
\endverse

\textnote{Repeat Chorus}

\endsong