\beginsong{I will survive}[by={Gloria Gaynor}]
\beginverse
At \[Am]first I was afraid, I was \[Dm]petrified,
Kept thinking \[G]I could never live without you \[C]by my side.
But then I \[F]spent so many nights, thinking \[Bm]how you did me wrong,
And I grew \[E]strong; and I learned \[E7]how to get along.
\endverse
\beginverse
And so you're \[Am]back, from outer \[Dm]space,
I just walked \[G]in to find you here, with that sad \[C]look upon your face.
I should have \[F]changed that stupid lock, I should have \[Bm]made you leave your key,
If I had \[E]known for just one second, you'd be \[E7]back to bother me.
\endverse
\beginverse*
\textnote{Chorus 1:}
Go on now, \[Am]go; walk out the \[Dm]door;
Just turn a\[G]round now, 'cos you're not \[C]welcome any more.
\[F] Weren't you the one who tried to \[Bm]hurt me with goodbye?
Did you think I'd \[E]crumble; did you think I'd \[E7]lay down and die?

Oh no, not \[Am]I; I will sur\[Dm]vive,
Oh, as \[G]long as I know how to love, I \[C]know I'll stay alive.
I've got \[F]all my life to live, and I've got \[Bm]all my love to give,
And I'll sur\[E]vive, I will sur\[E7]vive, I will sur\[Am]vive...
\endverse
\beginverse*
\textnote{Interlude:}
\[Am]  \[Dm]  \[G]  \[C] \[F]  \[Bm]  \[E]  \[E7]
\endverse
\beginverse
I prayed the \[Am]Lord to give me strength not to \[Dm]fall apart,
Though I tried \[G]hard to mend the pieces of my \[C]broken heart.
And I spent \[F]oh, so many nights, just feeling \[Bm]sorry for myself,
I used to \[E]cry, but now I \[E7]hold my head up high.
\endverse
\beginverse
And you'll see \[Am]me with somebody \[Dm]new,
I'm not that \[G]chained up little person, still in \[C]love with you.
And so you \[F]felt like dropping in and just ex\[Bm]pect me to be free,
Well, now I'm \[E]saving all my loving, for some\[E7]one who's loving me.
\endverse
\beginverse*
\textnote{Chorus 2:} 
Go on now, \[Am]go; walk out the \[Dm]door;
Just turn a\[G]round now, 'cos you're not \[C]welcome any more.
\[F] Weren't you the one who tried to \[Bm]crush me with goodbye?
Did you think I'd \[E]crumble; did you think I'd \[E7]lay down and die?

Oh no, not \[Am]I; I will sur\[Dm]vive,
And as \[G]long as I know how to love, I \[C]know I'll stay alive.
I've got \[F]all my life to live, and I've got \[Bm]all my love to give,
And I'll sur\[E]vive, \[E7]I I I will sur\[Am]vive...
\endverse
\beginverse*
\[Am] \[Dm]
\textnote{Optional: Repeat from Chorus 1 to end of song}
\endverse
\endsong