\beginsong{I will survive spoof "I will derive"}[by={Anonymous}]
\beginverse
At \[Am]first I was afraid, what could the \[Dm]answer be?
It said \[G]given this position find vel\[C]ocity.
So I \[F]tried to work it out but I \[Bm]knew that I was wrong.
I \[E]struggled; I cried: "the problem \[E7]shouldn't take this long!"
\endverse
\beginverse
I tried to \[Am]think, control my \[Dm]nerve...
It's evi\[G]dent that speed's tangential to that \[C]time-position curve
This \[F]problem would be mine
If I just \[Bm]knew that tangent line, but what to \[E]do? Show me a \[E7]sign!
\endverse
\beginchorus
So I thought \[Am]back: to calcu\[Dm]lus,
Way back to \[G]Newton and to Leibniz
And to \[C]problems just like this.
\[F] And just like that when I had \[Bm]given up all hope
I said \[E]nope. There's just one \[E7]way to find that slope!

And so now \[Am]I, I will \[Dm]derive!
Find the der\[G]ivative of x's position \[C]with respect to time.
It's as \[F]easy as can be; just have to \[Bm]take dx/dt
I will der\[E]ive, I will der\[E7]ive, hey \[Am]hey!
\endchorus
\beginverse*
\textnote{Interlude:}
\[Am]  \[Dm]  \[G]  \[C] \[F]  \[Bm]  \[E]  \[E7]
\endverse
\beginverse
And then I \[Am]went ahead to the \[Dm]second part
But as I \[G]looked at it I wasn't quite sure \[C]how to start:
It was \[F]asking for the time at \[Bm]which velocity
was at a \[E]maximum. And I was \[E7]thinking, "Woe is me!"
\endverse
\beginverse
But \[Am]then I though: "This much I \[Dm]know
I gotta \[G]find acceleration, set it equal to \[C]zero.
\[F] Now if I only knew what the \[Bm]function was for "A"...
\[E] I guess I'm gonna have to \[E7]solve for it some way."
\endverse
\beginverse*
\textnote{Repeat Chorus, Interlude}
\textnote{Repeat Chorus, replace last line with:}
I will der\[E]ive, I will der\[E7]ive, I will der\[Am]ive!
\endverse
\endsong
