\beginsong{I would do anything for love}[by={Meat Loaf}]
\beginverse (**SONG STILL A BIT TOO LONG)
And I would do \[D]anything for \[A]love
I'd run right into \[D]hell and back \[A] \[G]
I would do \[D]anything for \[A]love
I'd never lie to you and \[D]that's a fact \[A] \[G]
But I'll \[Bm]never forget the way you \[F#m]feel right now,
Oh \[G]no, no \[A]way. And I would do \[D]anything for \[A]love
Oh I would do \[D]anything for \[A]love. I would do \[D]anything for \[A]love, 
but I won't do \[G]that. \[A] No, I won't do \[D]that \[D] \[D]
\endverse

\beginverse
\[Bm] Some days it don't come easy. \[G] Some days it don't come hard
\[Em] Some days it don't come at all, and \[D]these are the days that never end
\[Bm] Some nights you're breathing fire. \[G] Some nights you're carved in ice
\[Em] Some nights you're like nothing I've ever \[D]seen before or will again
\endverse

\beginverse
\[G] Maybe I'm \[D]crazy, but it's \[Bm]crazy and it's \[A]true
\[G] I know you can \[D]save me, no one else can \[Bm]save me now but \[A]you
\endverse

\beginverse
\[Em] As long as the planets are turning. \[Gdim] As long as the stars are burning
\[G] As long as your dreams are coming \[A]true
You'd better believe it, that I would do
\endverse

\beginverse
\[D]Anything for \[A]love. And I'll be there 'til the \[D]final act \[A] \[G]
I would do \[D]anything for \[A]love, and I'll take a vow and \[D]seal a pact \[A] \[G]
But I'll \[Bm]never forgive myself if \[F#m]we don't go all the \[G]way, to\[A]night
I would do \[D]anything for \[A]love. Oh, I would do \[D]anything for \[A]love
Oh, I would do \[D]anything for \[A]love, but I won't do \[G]that
\[A] No, I won't do...
\endverse

\beginverse
\[Bm] Some days I pray for silence. \[G] Some days I pray for soul
\[Em] Some days I just pray to the god of \[D]sex and drums and rock 'n' roll
\[Bm] Some nights I lose the feeling. \[G] Some nights I lose control
\[Em] Some nights I just lose it all when I \[D]watch you dance and the thunder rolls
\endverse

\beginverse
\[G] Maybe I'm \[D]lonely, that's all I'm \[Bm]qualified to \[A]be
\[G] That's just one and \[D]only, one and only \[Bm]promise I can \[A]keep
\endverse

\beginverse
\[Em] As long as the wheels are turning. \[Gdim] As long as the fires are burning
\[G] As long as your prayers are coming \[A]true
You'd better believe it, that I would do
\endverse

\beginverse
\[D]Anything for \[A]love
And you know it's true and \[D]that's a fact \[A] \[G]
I would do \[D]anything for \[A]love, and there'll never be no \[D]turning back \[A] \[G]
But I'll \[Bm]never do it better than I \[F#m]do it with you. So \[G]long, so \[A]long
I would do \[D]anything for \[A]love. Oh, I would do \[D]anything for \[A]love
I would do \[D]anything for \[A]love, but I won't do \[G]that
No, \[A]no, no, I won't do...
\endverse

\beginverse
Will you \[D]raise me \[G]up? will you \[A]help me down?
Will you \[D]get me right \[G]out of this \[A]godforsaken town?
Will you \[D]make it all a \[G]little less \[A]cold?
I can do \[G]that, \[A] I can do...
\endverse

\beginverse
\[D]Anything for \[A]love. Oh, I would do \[D]anything for \[A]love
I would do \[D]anything for \[A]love, but I won't do \[G]that
\[A] No, I won't do \[D]that
\endverse
\endsong