\beginsong{Losing My Religion}[by={R.E.M.}]
\beginverse*
\nolyrics{Intro: \[F] \[Dm] \[G] \[Am] \[Am/B] \[Am/C] \[Am/D] \[Am]}
\nolyrics{\hspace{.9cm} \[F] \[Dm] \[G] \[Am] \[G]}
\endverse 	
\beginverse
Oh \[Am]life, is bigger \[Em]
It's bigger than you
And you are \[Am]not me.
The lengths that I will \[Em]go to,
The distance in your \[Am]eyes, \[Em]
Oh no I've said too \[Dm]much,
I set it \[G]up.
\endverse
\beginchorus
That's me in the \[Am]corner,
That's me in the \[Em]spot-light
Losing my re\[Am]ligion.
Trying to \[Em]keep up with you.
And I don't know if I can do it. \[Em]
Oh no I've said too \[Dm]much,
I haven't said e\[G]nough.
\endchorus
\beginverse*
\textnote{Bridge:}
I th\[Am]ought that I heard you \[F]laughing,
I thoug\[Dm]ht that I h\[G]eard you s\[Am]ing. \[Am/B] \[Am/C] \[Am/D]
\[Am]I th\[F]ink I thought I \[Dm]saw \[G]you \[Am]try. \[G]
\endverse
\beginverse
Every whis\[Am]per, of every waking \[Em]hour
I'm choosing my con\[Am]fessions,
Trying to \[Em]keep an eye on you
Like a \[Am]hurt, lost and blinded fool, fool \[Em]
Oh no I've said too \[Dm]much,
I set it \[G]up.
\endverse
\beginverse
Consider \[Am]this, consider this, 
The \[Em]hint of the century,
Consider \[Am]this: the slip
That \[Em]brought me to my knees failed.
\[Am]What if all these fantasies
Come \[Em] flailing around?
Now I've \[Dm]said too \[G]much.
\endverse
\textnote{Repeat Bridge}
\beginverse*
But \[C]that was just a \[Dm]dream,
\[C]That was just a \[Dm]dream.
\endverse
\textnote{Repeat Chorus}
\textnote{Repeat Bridge}
\beginverse*
But \[F]that was just a \[Dm]dream\[G],
\[Am]Try, \[Am/B]cry, \[Am/C]why, \[Am/D]try. \[Am]
\[F]That was just a dream, \[Dm] j\[G]ust a dr\[Am]eam, just a d\[G]ream, dream.
\endverse
\endsong
