\beginsong{Lumberjack song}[by={Monty Python}]
\beginverse*\singlespacing
\textnote{Narrated}
I didn't want to be a barber anyway.
I wanted to be... a Lumberjack

Leaping from tree to tree! As they float down the mighty rivers of British Columbia!
The Giant Redwood!
The Larch!
The Fir
The Mightly Scotts Pine!
The smell of fresh cut timber!
The crash of mighty trees.
With my best girlie by my side.
We'd sing! Sing! Sing!
\endverse

\beginverse
\[G]I'm a lumberjack and \[C]I'm O.K.
I \[D]sleep all night and I \[G]work all day.
\endverse

\beginchorus
\[G]He's a lumberjack and \[C]he's O.K.
He \[D]sleeps all night and he \[G]works all day.
\endchorus

\beginverse\memorize
I \[G]cut down trees, I \[C]eat my lunch, I \[D]go to the Lavat'\[G]ry
On \[G]Wednesdays I go \[C]shopping
And have \[D]buttered scones for \[G]tea.
\endverse

\beginverse
He ^cuts down trees, he ^eats his lunch, he ^goes to the Lavat'^ry
On ^Wednesdays he goes ^shopping
And has ^buttered scones for ^tea.
\endverse
\textnote{Repeat Chorus}

\beginverse
I ^cut down trees, I ^skip and jump, I ^like to press wild ^flowers
I ^put on women's ^clothing
And ^hang around in ^bars.
\endverse

\beginverse
He ^cuts down trees, he ^skips and jumps, he ^likes to press wild ^flowers
He ^puts on women's ^clothing
And ^hangs around in ^bars?
\endverse

\textnote{Repeat Chorus}

\beginverse
I ^cut down trees, I ^wear high heels
Susp^endies and a ^bra
I ^wish I'd been a ^girlie
Just ^like my dear ^mamma
\endverse

\beginverse
He ^cuts down trees
He ^wears high heels?
Susp^endies ... and a ^bra?
\endverse

\textnote{Repeat Chorus}

\beginverse
I ^cut down trees, I ^wear high heels, sus^pendies and a ^bra
I ^wish I'd been a ^girlie
Just ^like my dear mamm^a
\endverse

\textnote{Repeat Chorus}
\endsong
