\beginsong{Me \& Bobby McGee}[by={Janis Joplin}]
\beginverse
\[G] Busted flat in Baton Rouge, waiting for a train
And I's feeling nearly as faded as my \[D]jeans.
Bobby thumbed a diesel down just before it rained,
It rode us all the way to New Or\[G]leans.
I pulled my harp from and my dirty red bandanna,
I was playing soft while \[G7]Bobby sang the \[C]blues.
Windshield wipers slapping time, I was \[G]holding Bobby's hand in mine,
\[D7]We sang every song that driver knew.
\endverse
\beginchorus
\[C]Freedom is just another word for \[G]nothing left to lose,
\[D7]Nothing don't mean nothing honey if it ain't \[G]free, now now.
And \[C]feeling good was easy, Lord, \[G]when he sang the blues,
You know \[D7]feeling good was good enough for me,
Good enough for me and my Bobby Mc\[G]Gee. \[A]
\endchorus
\beginverse
From the Kentucky coal mines to the California sun,
Hey, Bobby shared the secrets of my \[E]soul.
Through all kinds of weather, through everything that we done,
Hey Bobby baby kept me from the \[A]cold.
One day up near Salinas, Lord, I let him slip away,
He's looking for that \[A7]home and I hope he \[D]finds it,
But I'd trade all of my tomorrows for one \[A]single yesterday
To be \[E7]holding Bobby's body next to mine.
\endverse
\beginchorus
\[D]Freedom is just another word for \[A]nothing left to lose,
\[E7]Nothing, that's all that Bobby left \[A]me, yeah,
But \[D]feeling good was easy, Lord, \[A]when he sang the blues,
Hey, \[E7]feeling good was good enough for me, hmm hmm,
Good enough for me and my Bobby Mc\[A]Gee.
\endchorus
\beginverse*
La la la, la la la la, la la la, la la la la
La la la la la Bobby Mc\[E]Gee.
La la la la la, la la la la la
La la la la la, Bobby Mc\[A]Gee, la.
\endverse
\endsong