\beginsong{No Woman No Cry}[by={Bob Marley}]
\beginverse*\singlespacing
\nolyrics{Intro: \[C] \[G] \[Am] \[F] \[C] \[F7] \[Am7] \[D9] \[C]}
\endverse

\beginverse
(\[C] No, \[G]woman, no cry-\[Am]y \[F]
\[C] No, \[F7]woman, no \[C]cry \[G]) x 2
\endverse

\beginverse\memorize
'said - 'said 
\[C] 'said I re\[G]member \[Am]when we used to sit \[F]
\[C] In a government \[G]yard in \[Am]Trenchtown \[F]
\[C] Oba - oba\[G]serving \[Am]the hypocrites \[F]
As they \[C]would mingle \[G]with the good people \[Am]we meet! \[F]
\[C] Good friends we \[G]have, oh, \[Am]good friends we have \[F]lost
\[C] Al\[G]ong the \[Am]way, \[F]yeah!
\[C]In this \[G]great future, you \[Am]can't forget your \[F]past;
\[C] So \[G]dry your tears, I sa\[Am]y \[F]
\endverse

\beginchorus
    \[C] No, \[G]woman, no cry \[Am] \[F]
    \[C] No, \[F7]woman, no \[C]cry \[G]
    \[C] Dear little \[G]darlin', don't \[Am]shed no \[F]tears:
    \[C] No, \[F7]woman, no \[C]cry. \[G]
\endchorus
\beginverse
Said - said -
^ Said I re^member ^when we used to sit ^
^ In the government ^yard in ^Trenchtown! ^
^ And then ^Georgie would ^make the fire lights, ^
As it was ^ logwood ^burnin' through the ^night! ^
^ Then we would ^cook cornmeal ^porridge, ^
^ Of which I'll ^share with ^you, ooh. ^
^ My ^feet is my ^only carri^age
^So I've got to ^push on ^through.
But while I'm ^gone,
\endverse
\beginverse*
(\[C] Everything's gonna \[G]be all right!
\[Am] Everything's gonna \[F7]be all right, yeah!) x 4
\endverse
\beginchorus
    \[C] No, \[G]woman, no cry \[Am] \[F]
    \[C] No, \[F7]woman, no \[C]cry \[G]
    \[C] oh no little \[G]sister, \[Am] don't shed no \[F]tears:
    \[C] No, \[F7]woman, no \[C]cry. \[G]
\endchorus
\endsong
