\beginsong{Puff the Magic Dragon}[by={Peter Paul and Mary}]
\capo{2}
\beginverse
\[G]Puff, the magic \[Bm]dragon \[C]lived by the \[G]sea
And \[C]frolicked in the \[G]autumn mist in a \[Em]land called \[A7]Honah \[D]Lee
\[G]Little Jackie \[Bm]Paper \[C]loved that rascal \[G]Puff,
And \[C]brought him strings and \[G]sealing \[Em]wax and \[A7]other \[D7]fancy \[G]stuff. \[D7]Oh 
\endverse

\beginchorus
\[G]Puff, the magic \[Bm]dragon \[C]lived by the \[G]sea
And \[C]frolicked in the \[G]autumn mist in a \[Em]land called \[A7]Honah \[D]Lee
\[G]Puff, the magic \[Bm]dragon \[C]lived by the \[G]sea
And \[C]frolicked in the \[G]autumn mist in a \[Em]land called \[D]Honah \[G]Lee
\endchorus

\beginverse
\[G]Together they would \[Bm]travel on a \[C]boat with billowed \[G]sail
\[C]Jackie kept a \[G]lookout perched on \[Em]Puff's gig\[A7]antic \[D]tail,
\[G]Noble kings and \[Bm]princes would \[C]bow whene'er they \[G]came,
\[C]Pirate ships would \[G]lower their flags when \[Em]Puff roared \[A7]out his \[D]name. \[D7]Oh! 
\endverse
\textnote{Repeat Chorus}
\beginverse
A \[G]dragon lives for\[Bm]ever but \[C]not so little \[G]boys
\[C]Painted wings and \[G]giant strings make \[Em]way for \[A7]other \[D]toys.
\[G]One grey night it \[Bm]happened, Jackie \[C]Paper came no \[G]more
And \[C]Puff that mighty \[G]dragon, he \[Em]ceased his \[A7]fearless \[D]roar. 

His \[G]head was bent in \[Bm]sorrow, green \[C]scales fell like \[G]rain,
\[C]Puff no longer \[G]went to play a\[Em]long the \[A7]cherry \[D]lane.
With\[G]out his lifelong \[Bm]friend, \[C]Puff could not be \[G]brave,
So \[G]Puff that mighty \[G]dragon sadly \[Em]slipped int\[A7]o his \[D]cave. \[D7]Oh! 
\endverse
\textnote{Repeat Chorus}
\endsong
