\beginsong{Somewhere Over The Rainbow / What A Wonderful World}[by={Israel Kamakawiwo'ole}]
\beginverse*
\nolyrics{Intro: \[G] \[Gmaj7] \[Em] \[C] \[G] \[D] \[Em] \[C] \[C9] \[C]}
\endverse
\beginverse*
\[G]Ooo… ooo… \[Bm]ooo… ooo… ooo… ooo… \[C]ooo… ooo… ooo… \[G]ooo...
\[C]Ooo… ooo… \[B7]ooo… ooo… ooo… \[Em]ooo… ooo… ooo… \[C]ooo… ooo… ooo...
\endverse
\beginverse
\[G]Somewhere \[Bm]over the rainbow, \[C] way up \[G]high
\[C]And the \[G]dreams that you dream of
\[D]Once in a lulla\[Em]by \[C] 
\endverse
\beginverse
\[G]Somewhere \[Bm]over the rainbow, \[C] bluebirds \[G]fly,
\[C]And the \[G]dreams that you dream of
\[D]Dream really do come \[Em]true \[C]
\endverse
\beginverse
Some\[G]day I'll wish upon a star
And \[D]wake up where the clouds are far
Be\[Em]hind \[C]me….
Where \[G]troubles melt like lemon drops
\[D]High above the chimney tops
That's \[Em]where you'll \[C]find me. 
\endverse
\beginverse
\[G]Somewhere \[Bm]over the rainbow, \[C] bluebirds \[G]fly.
\[C]And the \[G]dreams that you dare to
\[D]Oh why, oh why can't \[Em]I? \[C]
\endverse
\textnote{What a wonderful world}
\beginverse
Well I see \[G]trees of \[Bm]green and, \[C]red roses \[G]too,
\[C] I'll watch them \[G]bloom \[B7] for me and \[Em]you
And I \[C]think to myself, \[D] what a wonderful \[Em]world \[C]
\endverse
\beginverse
Well I see \[G]skies of \[Bm]blue and I, \[C]see clouds of \[G]white
\[C] And the brightness of \[G]day \[B7] I like the \[Em]dark 
And I \[C]think to myself, \[D] what a wonderful \[G]world \[C] \[G]
\endverse
\beginverse
The \[D]colours of the rainbow so \[G]pretty in the sky
Are \[D]also on the faces of \[G]people passing by
I see \[C]friends shaking \[G]hands
Saying, \[C]"How do you \[G]do?"
\[C] They're really \[G]saying, 
\[C] I...I love \[D]you
\endverse
\beginverse
I hear \[G]babies \[Bm]cry and I, \[C] watch them \[G]grow,
\[C] They'll learn much \[G]more, \[B7] than we'll \[Em]know
And I \[C] think to myself, \[D] what a wonderful \[Em]world \[C]
\endverse
\textnote{Somewhere over the rainbow}
\beginverse
Some\[G]day I'll wish upon a star
\[D]Wake up where the clouds are far Be\[Em]hind \[C]me...
Where \[G]troubles melt like lemon drops
\[D]High above the chimney tops
That's \[Em]where you'll \[C]find me.
\endverse
\beginverse
Oh \[G]somewhere \[Bm]over the rainbow, \[C] way up \[G]high.
\[C]And the \[G]dreams that you dare to
\[D]Why oh why can't \[Em]I? \[C]
\endverse
\beginverse*
\[G]Ooo… ooo… \[Bm]ooo… ooo… ooo… ooo… \[C]ooo… ooo… ooo… \[G]ooo...
\[C]Ooo… ooo… \[B7]ooo… ooo… ooo… \[Em]ooo… ooo… ooo… \[C]ooo… ooo…ooo \[G]
\endverse
\endsong