\beginsong{Summer of 69}[by={Bryan Adams}]
\beginverse*\singlespacing
{\nolyrics Intro: \[D] \[A] \[D] \[A]}
\endverse
\beginverse
\[D] I  got my first real six-string
\[A] Bought it at the five-and-dime
\[D] Played it 'til my fingers bled
\[A] It was the summer of '69
\endverse
\beginverse
\[D] Me and some guys from school
\[A] Had a band and we tried real hard.
\[D] Jimmy quit, Jody got married
\[A] I should've known we'd never get far
\endverse
\beginverse
\[Bm] Oh, when I \[A]look back now
\[D] That summer seemed to \[G]last forever
\[Bm] And if I \[A]had the choice
\[D] Yeah, I'd always \[G]wanna be there
\[Bm] Those were the \[A]best days of my \[D]life \[A]
\endverse

\beginverse
\[D] Ain't no use in complainin'
\[A] When you've got a job to do
\[D] Spent my evening's down at the drive-in
\[A] And that's when I met you, yeah
\endverse

\beginchorus
\[Bm] Standin' on your \[A]mama's porch
\[D] You told me that you'd \[G]wait forever
\[Bm] Oh, and when you \[A]held my hand
\[D] I knew that it was \[G]now or never
\[Bm] Those were the \[A]best days of my \[D]life. Oh, \[A]yeah.
Back in the summer of \[D]'69, \[A] oh.
\endchorus

\beginverse
\[F] Man we were \[Bb]killin' time
We were \[C]young and restless
We \[Bb]needed to unwind
\[F] I guess \[Bb]nothin' can last \[C]forever, \[C]forever, no! \[D] \[A]
\[D] \[A]
\endverse
\beginverse
\[D] And now the times are changin'
\[A] Look at everything that's come and gone
\[D] Sometimes when I play that old six-string
\[A] I think about you, wonder what went wrong
\endverse
\textnote{Repeat Chorus}
\beginverse*
It was the summer of \[D]'69, oh, \[A]yeah.
Me and my baby in \[D]'69, \[A] oh. \[D]
It was the \[A]summer, the summer, the summer of \[D]'69, \[A] yeah.
\endverse
\endsong
