\beginsong{Viva la vida}[by={Coldplay}]
\beginverse*
\nolyrics{Intro: \[C] \[D] \[G] \[Em] (x2)}
\endverse
\beginverse\memorize
I used to \[C]rule the \[D]world. Seas would \[G]rise when I gave the \[Em]word
Now in the morning I \[C]sleep a\[D]lone. Sweep the \[G]streets I used to \[Em]own 
\endverse
\beginverse*
\[C] \[D] \[G] \[Em] \[(x2)]
\endverse
\beginverse
I used to ^roll the ^dice. Feel the ^fear in my enemy's ^eyes
Listen as the ^crowd would ^sing
"Now the ^old king is dead! Long live the ^king!"
\endverse
\beginverse
One minute I ^held the ^key. Next the ^walls were closed on ^me
And I discovered that my ^castles ^stand
Upon ^pillars of salt and ^pillars of sand
\endverse
\beginchorus
I \[C]hear Jerusalem \[D]bells are ringing. \[G]Roman Cavalry \[Em]choirs are singing
\[C]Be my mirror, my \[D]sword and shield. My \[G]missionaries in a \[Em]foreign field
\[C]For some reason I \[D]can't explain. \[G]Once you're gone there was \[Em]never
Never an \[C]honest \[D]word. But that was \[G]when I ruled the \[Em]world
\endchorus
\beginverse*
\[C] \[D] \[G] \[Em] \[(x2)]
\endverse
\beginverse
It was the wicked and ^wild ^wind. Blew down the ^doors to let me ^in
Shattered windows and the ^sound of ^drums
People ^couldn't believe what ^I'd become
\endverse
\beginverse
Revolution^aries ^wait. For my ^head on a silver ^plate
Just a puppet on a ^lonely ^string
Oh ^who would ever want to be ^king?
\endverse
\beginchorus
I \[C]hear Jerusalem \[D]bells are ringing. \[G]Roman Cavalry \[Em]choirs are singing
\[C]Be my mirror, my \[D]sword and shield. My \[G]missionaries in a \[Em]foreign field
\[C]For some reason I \[D]can't explain. I \[G]know Saint Peter won't \[Em]call my name
Never an \[C]honest \[D]word. But that was \[G]when I ruled the \[Em]world
\endchorus
\beginverse*
\[C] \[D] \[G] \[Em] \[(x2)]
Woah… ^oh... ^oh... woah... ^oh… ^oh...
Woah... ^oh... ^oh... woah... ^oh… ^oh...
\endverse
\textnote{Repeat Chorus}
\endsong